---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# retel

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![R-CMD-check](https://github.com/markean/retel/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/markean/retel/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Overview

retel implements the regularized exponentially tilted empirical likelihood method.
The proposed method removes the convex hull constraint using a novel regularization technique, providing a suitable pseudo-likelihood for Bayesian inference.

The following functions enable users to set estimating functions by providing data and parameters:

* `etel()` computes exponentially tilted empirical likelihood without regularization.
* `retel()` computes regularized exponentially tilted empirical likelihood with regularization parameters.

This repository accompanies the research paper titled 'Regularized Exponentially Tilted Empirical Likelihood for Bayesian Inference,' available on [arXiv](https://arxiv.org/abs/2312.17015).
The `retel-paper` folder contains code and additional resources related to the paper.
This work was supported by the U.S. National Science Foundation under Grants No. [SES-1921523](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1921523) and [DMS-2015552](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2015552).


## Installation

You can install the latest stable release of retel from CRAN.

```{r, eval = FALSE}
install.packages("retel")
```

### Development version

You can install the development version of retel from GitHub.

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("markean/retel")
```

## Usage

```{r, message = FALSE}
library(retel)

# Generate data
set.seed(63456)
x <- rnorm(100)

# Define an estimating function (ex. mean)
fn <- function(x, par) {
  x - par
}

# Set parameter value
par <- 0

# Set regularization parameters
mu <- 0
Sigma <- 1
tau <- 1

# Call the retel function to compute the log-likelihood ratio. The return value
# contains the optimization results as the attribute 'optim'.
retel(fn, x, par, mu, Sigma, tau)
```
